Atlantis to SS for California Current sardines and hake: full fishing and climate scenario

### 2019-09-27 SardinesHakeatlantisom2SStest.Rmd
correct folder name and turn on write SS block

Now we test the `atlantisom` to SS workflow with a new California Current run that includes climate forcing, recruitment variability, and the fishing scenario outlined for our project in Norway: "output_CC_2063_OA_OFF_222".

>>>>

Now we test the `atlantisom` to SS workflow with a new California Current run that includes climate forcing, recruitment variability, and the fishing scenario outlined for our project in Norway: "output_CC_2063_OA_OFF_22".
